---
title: "Trial Tracker Dashboard"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    includes:
      in_header: GA_Script.html
runtime: shiny
---

```{r setup, context = 'setup'}

# TODO

#Front end
# 1) Add more error handling controls for on adding IDS (pattern match), especially NIHR

#Backend
# 1) PURGE dot/space from Guideline number field - rename ID fields in registry_fields equal to names in Trial_Ids
# 2) Move formatting/manipulation from markdown back to update script (and possibly back to initial input script from s-sheet)

library(tidyverse)
library(DBI)
library(flexdashboard)
library(DT)
library(compareDF)
library(shiny)
library(shinybusy)

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

con <- dbConnect(RSQLite::SQLite(), "RSQLite_Data/TrialTracker-db.sqlite")

Ids <- dbReadTable(con, "Trial_Ids")

clean_UTF <- function(x){
  iconv(x, "UTF-8", "UTF-8", sub = "")
}

#Regex patterns
NCT_pattern <- "NCT[0-9]{8}"
EU_pattern <- "[0-9]{4}-[0-9]{6}-[0-9]{2}"
ISRCTN_pattern <- "ISRCTN[0-9]{8}"
NIHR_pattern <- "(NIHR[0-9]{0,6})|(RP-PG-[0-9]{4}-[0-9]{4,5})|([0-9]{2,3}[/-][0-9]{2,4}[/-][0-9]{2,4})|(^ICA-.*-[0-9]{3})"


```

Live Trial Info
======================================================

**Last refreshed: `r file.info("RSQLite_Data/TrialTracker-db.sqlite")$mtime`**

Row {.tabset .tabset-fade}
--------------------------------------------------------

### ClinicalTrials.gov

```{r CTGtable}

#create added_dates
NCT_dates <- dbReadTable(con, "NCT") %>% 
  group_by(NCTId) %>% 
  summarise("Date Added" = as_date(min(Query_Date-1)))

dbReadTable(con, "NCT") %>%
  filter(NCTId %in% Ids$NCT_Ids) %>% 
  left_join(NCT_dates) %>% # Add date added field
  slice_max(Query_Date, n = 1, with_ties = TRUE) %>%
  select(-Query_Date, -SeeAlsoLinkURL) %>%
  select(Program, Guideline.number, `Date Added`, everything()) %>% # reorder 
  mutate(across(.fns = clean_UTF)) %>% 
  mutate(across(c(PrimaryCompletionDate:LastUpdatePostDate),
                \(x) as_date(parse_date_time(x, c('ymd', 'bdy'), truncated = 1)))) |> 
  rename(
    "Guideline" = Guideline.number,
    `NCT ID` = NCTId,
    `Org Study ID` = OrgStudyId,
    Title = BriefTitle,
    Status = OverallStatus,
    `Primary Completion Date` = PrimaryCompletionDate,
    `Completion Date` = CompletionDate,
    `Results Submit Date` = ResultsFirstSubmitDate,
    `Results Post Date` = ResultsFirstPostDate,
    `Last Update` = LastUpdatePostDate,
  ) %>%
  arrange(desc(`Date Added`), Program, Guideline, `NCT ID`) %>% 
  distinct() |> 
  datatable(options = list(bPaginate = FALSE, scrollY = TRUE),
            filter = "top"
            )
```

### ISRCTN

```{r ISRCTNtable}

#create added_dates
ISRCTN_dates <- dbReadTable(con, "ISRCTN") %>% 
  group_by(ISRCTN_No) %>% 
  summarise("Date Added" = as_date(min(Query_Date-1)))

dbReadTable(con, "ISRCTN") %>%
  filter(ISRCTN_No %in% Ids$ISRCTN_Ids) %>% 
  left_join(ISRCTN_dates) %>% 
  slice_max(Query_Date, n = 1, with_ties = TRUE) %>%
  select(-Query_Date) %>%
  select(Program, Guideline.number, `Date Added`, everything()) %>% # reorder 
  mutate(across(.fns = clean_UTF),
         Results_date_completed = dmy(Results_date_completed),
         Results_date_posted = dmy(Results_date_posted),
         Results_date_first_publication = dmy(Results_date_first_publication)) %>% 
  rename(
    "Guideline" = Guideline.number,
    `ISRCTN ID` = ISRCTN_No,
    Title = Public_Title,
    `Scientific Title` = Scientific_Title,
    `Recruitment Status` = Recruitment_Status,
    `Results completed date` = Results_date_completed,
    `Results URL` = Results_url_link,
    `Results summary` = Results_summary,
    `Results posted date` = Results_date_posted,
    `Results published date` = Results_date_first_publication
  ) %>%
  arrange(desc(`Date Added`), Program, Guideline, `ISRCTN ID`) %>%
  distinct() |> 
  datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
```

### NIHR

``` {r NIHRtable}

#create added_dates
NIHR_dates <- dbReadTable(con, "NIHR") %>% 
  group_by(project_id) %>% 
  summarise("Date Added" = as_date(min(Query_Date-1)))

dbReadTable(con, "NIHR") %>%
  mutate("project_id_filter" = str_replace_all(project_id, "[^\\d]", "")) %>% 
  filter(project_id_filter %in% str_replace_all(Ids$NIHR_Ids, "[^\\d]", "")) %>% 
  select(-project_id_filter) %>% 
  slice_max(Query_Date, n = 1, with_ties = TRUE) %>%
  select(-Query_Date) %>%
  left_join(NIHR_dates) %>%
  select(Program, Guideline.number, `Date Added`, everything()) %>% # reorder
  mutate(across(.fns = clean_UTF)) %>%
  rename(
    "Guideline" = Guideline.number,
    `NIHR ID` = project_id,
    `Project Title` = project_title,
    Status = project_status,
    `End Date` = end_date
  ) %>%
  arrange(desc(`Date Added`), Program, Guideline, `NIHR ID`) %>% 
  distinct() |> 
  datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")

```

### Clinicaltrials.eu

``` {r EUtable}

#create added_dates
EU_dates <- dbReadTable(con, "EU") %>% 
  group_by(EU_Ids) %>% 
  summarise("Date Added" = as_date(min(Query_Date-1)))

dbReadTable(con, "EU") %>%
  mutate("short_id" = str_sub(`X_id`, 1, 14)) %>% 
  filter(short_id %in% Ids$EU_Ids) %>% 
  left_join(EU_dates) %>% 
  slice_max(Query_Date, n = 1, with_ties = TRUE) %>%
  select(
    -Query_Date, -a31_title_of_the_trial_for_lay_people_in_easily_understood_ie_nontechnical_language, -EU_Ids, -short_id
  ) %>%
  select(Program, Guideline.number, `Date Added`, everything()) %>% # reorder 
  mutate(across(.fns = clean_UTF)) %>% 
  distinct() %>% 
  rename(
    "Guideline" = Guideline.number,
    `Clinicaltrials.eu ID` = `X_id`,
    `End of Trial Status` = p_end_of_trial_status,
    Title = a3_full_title_of_the_trial,
    `Abbreviated Title` = a32_name_or_abbreviated_title_of_the_trial_where_available,
    `Sponsor ID` = a41_sponsors_protocol_code_number
  ) %>%
  arrange(desc(`Date Added`), Program, Guideline, `Clinicaltrials.eu ID`) %>% 
  distinct() |> 
  datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")

```



Recent Status Changes
======================================================

**Last refreshed: `r file.info("RSQLite_Data/TrialTracker-db.sqlite")$mtime`**  
**Changes are from 31 days ago**

Row {.tabset .tabset-fade}
--------------------------------------------------------

### ClinicalTrials.gov

``` {r CGTmonthlychange}

new_df <- dbReadTable(con, "NCT") %>%
  filter(NCTId %in% Ids$NCT_Ids) %>% 
  slice_max(Query_Date, n = 1, with_ties = TRUE) |> 
  mutate(across(c(PrimaryCompletionDate:LastUpdatePostDate), \(x) as_date(parse_date_time(x, c('ymd', 'bdy'), truncated = 1))))

old_df <- dbReadTable(con, "NCT") %>%
  filter(Query_Date <= Sys.Date() - 31,
	NCTId %in% Ids$NCT_Ids) %>% 
  slice_max(Query_Date, n = 1, with_ties = TRUE) |> 
  mutate(across(c(PrimaryCompletionDate:LastUpdatePostDate), \(x) as_date(parse_date_time(x, c('ymd', 'bdy'), truncated = 1))))

compare_df(new_df,
           old_df,
           group_col = c("Guideline.number", "NCTId"),
           exclude = c("Query_Date"
                       , "Comments"
                       , "Condition"
                       , "BriefTitle"
                       , "Acronym"
                       , "PrimaryCompletionDate"
                       , "ResultsFirstSubmitDate"
                       , "SeeAlsoLinkURL"
                       ),
           stop_on_error = FALSE
           )$comparison_df %>%
  left_join(
      (new_df %>%
        select(BriefTitle,
               Program,
               Guideline.number,
               URL,
               NCTId,
               Condition,
               ResultsFirstSubmitDate,
               Acronym,
               Comments
               )),
    by = c("Program", "Guideline.number", "URL", "NCTId")
    ) %>% 
  mutate(URL2 = paste0("https://clinicaltrials.gov/ct2/show/", NCTId),
         Title = str_trunc(BriefTitle, 80),
         Condition = str_trunc(Condition, 30)) %>% 
  mutate(across(.fns = clean_UTF)) %>% 
  mutate(across(c(CompletionDate:LastUpdatePostDate), \(x) as_date(parse_date_time(x, c('ymd', 'bdy'), truncated = 1)))) |> 
  select(
    `Change` = chng_type,
    Program,
    "Guideline" = Guideline.number,
    URL = URL2,
    Acronym,
    Title,
    Condition,
    Status = OverallStatus,
    `Completion Date` = CompletionDate,
    `Results Submit Date` = ResultsFirstSubmitDate,
    `Last Update Date` = LastUpdatePostDate,
    Comments
  ) %>% 
  distinct() |> 
datatable(
  options = list(bPaginate = FALSE, scrollY = TRUE),
                 filter = "top")
  

```

### ISRCTN

``` {r ISRCTNmonthlychange}

new_df <- dbReadTable(con, "ISRCTN") %>%
  filter(ISRCTN_No %in% Ids$ISRCTN_Ids) %>% 
  slice_max(Query_Date, n = 1, with_ties = TRUE)

old_df <- dbReadTable(con, "ISRCTN") %>%
  filter(Query_Date <= Sys.Date() - 31,
 	 ISRCTN_No %in% Ids$ISRCTN_Ids) %>% 
  slice_max(Query_Date, n=1, with_ties = TRUE)

compare_df(new_df,
           old_df,
           group_col = c("Guideline.number", "ISRCTN_No"),
           exclude = c("Query_Date", "Comments"),
           stop_on_error = FALSE)$comparison_df %>%
  left_join(new_df) %>% 
  mutate(Title = str_trunc(Scientific_Title,75)) %>% 
  mutate(across(.fns = clean_UTF),
         Results_date_completed = dmy(Results_date_completed),
         Results_date_posted = dmy(Results_date_posted),
         Results_date_first_publication = dmy(Results_date_first_publication) 
         ) |> 
  select(Change = chng_type,
         Program,
         "Guideline" = Guideline.number,
         URL,
         Acronym,
         Title,
         Status = Recruitment_Status,
         `Results URL` = Results_url_link,
         `Results Summary` = Results_summary,
         `Results Completed` = Results_date_completed,
         `Results Posted` = Results_date_posted,
         `Results Published` = Results_date_first_publication) %>% 
  distinct() |> 
  datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")

```

### NIHR

``` {r NIHRmonthlychange}

new_df <- dbReadTable(con, "NIHR") %>% 
  mutate("project_id_filter" = str_replace_all(project_id, "[^\\d]", "")) %>% 
  filter(project_id_filter %in% str_replace_all(Ids$NIHR_Ids, "[^\\d]", "")) %>% 
  select(-project_id_filter) %>% 
  slice_max(Query_Date, n = 1, with_ties = TRUE)

old_df <- dbReadTable(con, "NIHR") %>%
  mutate("project_id_filter" = str_replace_all(project_id, "[^\\d]", "")) %>% 
  filter(project_id_filter %in% str_replace_all(Ids$NIHR_Ids, "[^\\d]", "")) %>% 
  select(-project_id_filter) %>% 
  filter(Query_Date <= Sys.Date() - 31) %>% 
  slice_max(Query_Date, n=1, with_ties = TRUE)

compare_df(
  new_df,
  old_df,
  group_col = c("Guideline.number", "project_id"),
  exclude = c("Query_Date", "Comments"),
  stop_on_error = FALSE
)$comparison_df %>%
  left_join(new_df) %>% 
  mutate(
         Title = str_trunc(project_title, 90)
         ) %>% 
  mutate(across(.fns = clean_UTF)) %>% 
  select(
    Change = chng_type,
    Program,
    "Guideline" = Guideline.number,
    URL,
    `NIHR ID` = project_id,
    Title,
    Status = project_status,
    `End Date` = end_date
         ) %>% 
  distinct() |> 
  datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")

```

### Clinicaltrials.eu

``` {r Clinicaltrials.eumonthlychange}

new_df <- dbReadTable(con, "EU") %>%
  filter(EU_Ids %in% Ids$EU_Ids) %>% 
  slice_max(Query_Date, n = 1, with_ties = TRUE)

old_df <- dbReadTable(con, "EU") %>%
  filter(Query_Date <= Sys.Date() - 30,
	 EU_Ids %in% Ids$EU_Ids
	) %>% 
  slice_max(Query_Date, n = 1, with_ties = TRUE)

compare_df(
  new_df,
  old_df,
  group_col = c("Guideline.number", "EU_Ids"),
  exclude = c("Query_Date", "Comments"),
  stop_on_error = FALSE
)$comparison_df %>%
  left_join(new_df) %>% 
  mutate(#`Query Date` = as.Date(Query_Date, origin = "1970-01-01"),
         Title = str_trunc(a3_full_title_of_the_trial, 90)) %>% 
  mutate(across(.fns = clean_UTF)) %>% 
  select(
    Change = chng_type,
    Program,
    "Guideline" = Guideline.number,
    URL,
    `EU ID` = EU_Ids,
    Status = p_end_of_trial_status,
    Acronym = a32_name_or_abbreviated_title_of_the_trial_where_available,
    Title) %>% 
  distinct() |> 
  datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")

```


No Changes in Last 6m
======================================================

**Last refreshed: `r file.info("RSQLite_Data/TrialTracker-db.sqlite")$mtime`**

Row {.tabset .tabset-fade}
--------------------------------------------------------

### ClinicalTrials.gov

``` {r nochangeCTG}

current <- dbReadTable(con, "NCT") %>%
  filter(Query_Date == as_date(max(Query_Date)))
         
old <- dbReadTable(con, "NCT") %>%
  filter(Query_Date == (as_date(max(Query_Date))-months(6)))

inner_join(current, old, by = names(current)[2:(ncol(current)-1)], keep = FALSE) %>% 
  select(-contains(".x")) %>% 
  select(-contains(".y")) %>%
  left_join(NCT_dates) %>% 
  select(Program, Guideline.number, `Date Added`, everything()) %>% # reorder 
  select(-SeeAlsoLinkURL) %>% 
  mutate(across(.fns = clean_UTF)) %>% 
  mutate(across(c(PrimaryCompletionDate:LastUpdatePostDate), \(x) as_date(parse_date_time(x, c('ymd', 'bdy'), truncated = 1)))) |> 
  rename(
    "Guideline" = Guideline.number,
    `NCT ID` = NCTId,
    `Org Study ID` = OrgStudyId,
    Title = BriefTitle,
    Status = OverallStatus,
    `Primary Completion Date` = PrimaryCompletionDate,
    `Completion Date` = CompletionDate,
    `Results Submit Date` = ResultsFirstSubmitDate,
    `Results Post Date` = ResultsFirstPostDate,
    `Last Update` = LastUpdatePostDate,
  ) %>%
  distinct() |> 
  datatable(options = list(bPaginate = FALSE, scrollY = TRUE),
            filter = "top"
            )

```

### ISRCTN

``` {r nochangeISRCTN}

current <- dbReadTable(con, "ISRCTN") %>%
  filter(Query_Date == as_date(max(Query_Date)))
         
old <- dbReadTable(con, "ISRCTN") %>%
  filter(Query_Date == (as_date(max(Query_Date))-months(6)))

inner_join(current, old, by = names(current)[2:(ncol(current)-1)], keep = FALSE) %>% 
  select(-contains(".x")) %>% 
  select(-contains(".y")) %>%
  left_join(ISRCTN_dates) %>% 
  select(Program, Guideline.number, `Date Added`, everything()) %>% # reorder 
  mutate(across(.fns = clean_UTF),
         Results_date_completed = dmy(Results_date_completed),
         Results_date_posted = dmy(Results_date_posted),
         Results_date_first_publication = dmy(Results_date_first_publication)) %>% 
  rename(
    "Guideline" = Guideline.number,
    `ISRCTN ID` = ISRCTN_No,
    Title = Public_Title,
    `Scientific Title` = Scientific_Title,
    `Recruitment Status` = Recruitment_Status,
    `Results completed date` = Results_date_completed,
    `Results URL` = Results_url_link,
    `Results summary` = Results_summary,
    `Results posted date` = Results_date_posted,
    `Results published date` = Results_date_first_publication
  ) %>%
  distinct() |> 
  datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")

```

### NIHR

``` {r nochangeNIHR}

current <- dbReadTable(con, "NIHR") %>%
  filter(Query_Date == as_date(max(Query_Date)))
         
old <- dbReadTable(con, "NIHR") %>%
  filter(Query_Date == (as_date(max(Query_Date))-months(6)))

inner_join(current, old, by = names(current)[2:(ncol(current)-1)], keep = FALSE) %>% 
  select(-contains(".x")) %>% 
  select(-contains(".y")) %>%
  left_join(NIHR_dates) %>% 
  select(Program, Guideline.number, `Date Added`, everything()) %>% # reorder 
  mutate(across(.fns = clean_UTF)) %>% 
  rename(
    "Guideline" = Guideline.number,
    `NIHR ID` = project_id,
    `Project Title` = project_title,
    Status = project_status,
    `End Date` = end_date
  ) %>%
  distinct() |> 
  datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")

```

### Clinicaltrials.eu

```{r nochangeEU}

current <- dbReadTable(con, "EU") %>%
  filter(Query_Date == as_date(max(Query_Date)))
         
old <- dbReadTable(con, "EU") %>%
  filter(Query_Date == (as_date(max(Query_Date))-months(6)))

inner_join(current, old, by = names(current)[2:(ncol(current)-1)], keep = FALSE) %>% 
  select(-contains(".x")) %>% 
  select(-contains(".y")) %>%
  left_join(EU_dates) %>% 
  select(-a31_title_of_the_trial_for_lay_people_in_easily_understood_ie_nontechnical_language, -EU_Ids
  ) %>%
  select(Program, Guideline.number, `Date Added`, everything()) %>% # reorder 
  mutate(across(.fns = clean_UTF)) %>% 
  distinct() %>% 
  rename(
    "Guideline" = Guideline.number,
    `Clinicaltrials.eu ID` = `X_id`,
    `End of Trial Status` = p_end_of_trial_status,
    Title = a3_full_title_of_the_trial,
    `Abbreviated Title` = a32_name_or_abbreviated_title_of_the_trial_where_available,
    `Sponsor ID` = a41_sponsors_protocol_code_number
  ) %>%
  distinct() |> 
  datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
  
```


Pubmed Publications
======================================================

**Last refreshed: `r file.info("RSQLite_Data/TrialTracker-db.sqlite")$mtime`**

Row {.tabset .tabset-fade}
--------------------------------------------------------

### ClinicalTrials.gov

``` {r CTGpubstable}

dbReadTable(con, "NCT_PM") %>%
  mutate(across(.fns = clean_UTF)) %>% 
  mutate(Query_Date = format(as.Date(as.numeric(Query_Date), origin = "1970-01-01"), "%Y/%m/%d"),
         abstract = str_trunc(abstract, 200)) %>%
  select(
    Program,
    "Guideline" = Guideline.number,
    `Query Date` = Query_Date,
    `Trial ID` = ID,
    PMID = pmid,
    `Publication DOI` = doi,
    Title = title,
    Abstract = abstract,
    Journal =  jabbrv,
    Condition = Short..working.title.
  ) %>%
  arrange(desc(`Query Date`)) %>% 
  distinct() |> 
  datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
```

### ISRCTN

``` {r ISRCTNpubstable}

dbReadTable(con, "ISRCTN_PM") %>%
  mutate(across(.fns = clean_UTF)) %>% 
  mutate(Query_Date = format(as.Date(as.numeric(Query_Date), origin = "1970-01-01"), "%Y/%m/%d"),
         abstract = str_trunc(abstract, 200)) %>%
  select(
    Program,
    "Guideline" = Guideline.number,
    `Query Date` = Query_Date,
    `Trial ID` = ID,
    PMID = pmid,
    `Publication DOI` = doi,
    Title = title,
    Abstract = abstract,
    Journal =  jabbrv,
    Condition = Short..working.title. ##cut this out due to non-UTF-8 character
  ) %>%
  distinct() |> 
  datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
```

### NIHR

``` {r NIHRpubstable}

dbReadTable(con, "NIHR_PM") %>%
  mutate(across(.fns = clean_UTF)) %>% 
  mutate(Query_Date = format(as.Date(as.numeric(Query_Date), origin = "1970-01-01"), "%Y/%m/%d"),
         abstract = str_trunc(abstract, 200)) %>%
  select(
    Program,
    "Guideline" = Guideline.number,
    `Query Date` = Query_Date,
    `Trial ID` = ID,
    PMID = pmid,
    `Publication DOI` = doi,
    Title = title,
    Abstract = abstract,
    Journal =  jabbrv,
    Condition = Short..working.title.
  ) %>%
  distinct() |> 
  datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
```

### Clinicaltrials.eu

``` {r EUpubstable}

if ("EU_PM" %in% dbListTables(con)) {
  dbReadTable(con, "EU_PM") %>%
    mutate(across(.fns = clean_UTF)) %>% 
    mutate(Query_Date = format(as.Date(as.numeric(Query_Date), origin = "1970-01-01"), "%Y/%m/%d"),
         abstract = str_trunc(abstract, 200)) %>%
    select(
      Program,
      "Guideline" = Guideline.number,
      `Query Date` = Query_Date,
      `Trial ID` = ID,
      PMID = pmid,
      `Publication DOI` = doi,
      Title = title,
      Abstract = abstract,
      Journal =  jabbrv,
      Condition = Short..working.title.,
    ) %>%
    distinct() |> 
    datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
}
```

Add/Remove Trials and Trial Comments
======================================================

Row {.tabset .tabset-fade}
--------------------------------------------------------

### Add Trial

There are two ways to add trials

1) Add one at a time, choosing the relevant registry button, completing the guideline number, trial id and url boxes then pressing 'add trial'
2) Add more than one trial at once by uploading a spreadsheet containing relevant details using the 'choose file' box

**Note that Trial ID reference number must be in the correct format. Eg:**

* Clinicaltrials.gov - "NCT03883230"  
* ISRCTN - "ISRCTN11735271"  
* NIHR - "14-158-02" or "14/158/02" or "RP-PG-0109-10056"  
* Clinicaltrials.eu - "2007-003673-21" (omit the last two letters designating country)


``` {r AddSingleTrial}

inputPanel("Add Single Trial",
  radioButtons(
    "registry_add",
    label = "",
    choices = c("Clinicaltrials.gov" = 'NCT_Ids',
                "ISRCTN" = 'ISRCTN_Ids',
                "NIHR" = 'NIHR_Ids',
                "Clinicaltrials.eu" = 'EU_Ids')
  ),
  selectInput('guideline_program_add', label = 'Enter program description', 
              choices = c("COVID", "IP", "Other"),
              selected = "COVID"),
  #textInput('guideline_program_add', label = 'Enter program description', placeholder = "e.g. COVID, IP, Other"),
  textInput('guideline_reference_add', label = 'Enter guideline number(s)', placeholder = "e.g. CG179"),
  textInput('ID_add', label = 'Enter Trial ID reference number', placeholder = " e.g. NCT03597750"),
  textInput('URL_add',
            label = 'Paste URL to trial page in registry',
            placeholder = "e.g. https://clinicaltrials.gov/ct2/show/NCT03597750",
            width = '200%'),
  actionButton("button_add", "Add trial"),
  uiOutput("single_result")
)

# mainPanel(textOutput('single_success'),
#           textOutput('single_fail'))

#NB NEED TO GO BACK AND PURGE DOT FROM FIELD - ADDED SQ BRACKETS AS WORKAROUND FOR NOW

sql_add <-
     "INSERT INTO Trial_Ids ([Program], [Guideline.number], [URL], [?registry]) VALUES (?program_value, ?Guideline_Reference, ?URL, ?ID)"

exp_add <- reactive({
  sqlInterpolate(
    con,
    sql_add,
    registry = SQL(input$registry_add),
    program_value = input$guideline_program_add,
    Guideline_Reference = input$guideline_reference_add,
    URL = str_trim(input$URL_add),
    ID = str_trim(input$ID_add))
})

observeEvent(input$button_add, {
  
  valid_id_check <- str_detect(input$ID_add, paste(c(NCT_pattern, EU_pattern, ISRCTN_pattern, NIHR_pattern), collapse = "|"))
  
  if(valid_id_check){
    
    shinybusy::show_modal_spinner(spin = "semipolar", color = "#344feb", text = "Adding Trial - please wait while the dashboard refreshes in background....")
    
    dbExecute(con, exp_add())
    
    source('Download_Trial_Info_no_PM_or_email.R')
    
    shinybusy::remove_modal_spinner()
    
    output$single_result <- renderText({
      HTML(as.character(div(style = "color: green;", 
                            "Trial Added! - please refresh browser to see trial details on Live Trial Info tab")))
      })
    
  } else if(!valid_id_check){
    
    output$single_result <- renderText({
      HTML(as.character(div(style = "color: red;", 
                            "Error - Invalid trial ID reference number, please check ID against the above approved formats")))
      })
    
  }
})

```

``` {r AddMultiTrial}

inputPanel("Add Multiple Trials via csv file",
  downloadButton('downloadtemplate', label = "Download template"),
  fileInput('uploadtemplate', label = 'Upload completed template', multiple = FALSE, accept = '.csv'),
  actionButton("button_add_multi", label = "Add trial spreadsheet"),
  uiOutput("multi_result"))


output$downloadtemplate <- downloadHandler(filename = function(){"trialuploadtemplate.csv"},
                                           content = function(file){
                                             write_csv(read_csv("trialuploadtemplate.csv",
                                                                col_types = cols(.default = col_character())),
                                                       file, na = "")})



to_add <- reactive({

  inFile <- input$uploadtemplate

  upload <- read_csv(file = inFile$datapath, col_types = cols(.default = col_character()))

})

#error check
observeEvent(input$uploadtemplate, {

  NCT_check <- str_detect(replace_na(to_add()$NCT_Ids, ''), NCT_pattern)
  EU_check <- str_detect(replace_na(to_add()$EU_Ids, ''), EU_pattern)
  ISRCTN_check <- str_detect(replace_na(to_add()$ISRCTN_Ids, ''), ISRCTN_pattern)
  NIHR_check <- str_detect(replace_na(to_add()$NIHR_Ids, ''), NIHR_pattern)
  Valid_ID <- {NCT_check|EU_check|ISRCTN_check|NIHR_check}
  errors <- which(Valid_ID == FALSE)

  output$errors <- renderText({paste0("errors = ", as.character(errors))})
  output$errors_length <- renderText({paste0("errors_length = ", as.character(length(errors)))})

  if (length(errors)>0){

  #output$multi_error <- renderText({paste("ERROR - missing or incorrect Trial ID on line(s)", as.character(errors))})
    output$multi_result <- renderText({
      HTML(as.character(div(style = "color: red;", 
                            paste("ERROR - Missing or incorrect Trial ID on line(s)", as.character(errors), 
                                  ", please correct these IDs and reupload the file"))))
    })

  } else if(length(errors) ==0){
    
    output$multi_result <- renderText({
      HTML(as.character(div(style = "color: green;", 
                            "File has passed input checks and is ready for upload")))
    })
    
  }

})

#observe event add
observeEvent(input$button_add_multi, {

  NCT_check <- str_detect(replace_na(to_add()$NCT_Ids, ''), NCT_pattern)
  EU_check <- str_detect(replace_na(to_add()$EU_Ids, ''), EU_pattern)
  ISRCTN_check <- str_detect(replace_na(to_add()$ISRCTN_Ids, ''), ISRCTN_pattern)
  NIHR_check <- str_detect(replace_na(to_add()$NIHR_Ids, ''), NIHR_pattern)
  Valid_ID <- {NCT_check|EU_check|ISRCTN_check|NIHR_check}
  multi_errors <- which(Valid_ID == FALSE)

  output$multi_errors <- renderText({paste0("multi_errors = ", as.character(multi_errors))})
  output$multi_errors_length <- renderText({paste0("multi_errors_length = ", as.character(length(multi_errors)))})

  if (length(multi_errors)==0){

  shinybusy::show_modal_spinner(spin = "semipolar", color = "#344feb", text = "Adding Trials - please wait while the dashboard refreshes in background....")

  DBI::dbAppendTable(con, "Trial_Ids", to_add())

  source('Download_Trial_Info_no_PM_or_email.R')
  
  shinybusy::remove_modal_spinner()

  #output$multi_success <- renderText("Multiple Trials Added! - please refresh browser to see trial details on Live Trial Info tab")
  output$multi_result <- renderText({
    HTML(as.character(div(style = "color: green;", 
                          "Multiple Trials Added! - please refresh browser to see trial details on Live Trial Info tab")))
  })

  } else if (length(multi_errors)>0){

  #output$multi_fail <- renderText("Please correct errors in trial ID numbers on upload sheet before resubmitting")
  output$multi_result <- renderText({
      HTML(as.character(div(style = "color: red;", 
                            "Error - Please correct errors in trial ID numbers on upload sheet before resubmitting")))
      })

  }

})


mainPanel(
  #textOutput('errors'),
  #textOutput('errors_length'),
  #textOutput('NIHR_check'),
  #textOutput('multi_errors'),
  #textOutput('multi_errors_length'),
  textOutput('multi_error'),
  textOutput('multi_fail'),
  textOutput('multi_success'))

```

### Remove or Archive Trial

Select relevant registry and trial ID reference number below, along with any comments if archiving.

'Archiving' moves the trial information from the live lists to the relevant archived trials list, where it will no longer be updated. 'Deleting' will remove the trial from the live lists and information will not be stored

``` {r Removetab}

inputPanel(
    radioButtons(
      "registry_remove",
      label = "Registry",
      choices = c(
        "Clinicaltrials.gov" = "NCT_Ids",
        "ISRCTN" = "ISRCTN_Ids",
        "NIHR" = "NIHR_Ids",
        "Clinicaltrials.eu" = "EU_Ids"
      )
    ),
    selectInput('ID_remove',
                label = 'Select Trial ID reference number',
                choices = ""),
    actionButton("button_delete", "Delete trial"),
    textInput("comments_archive", "Archive Comments"),
    actionButton("button_archive", "Archive trial")
  )

mainPanel(
  #textOutput("exp_archive"),
  #textOutput("exp_delete"),
  textOutput("success_delete"),
  textOutput("success_archive")
  )

observeEvent(input$registry_remove, {

  choices_list <- dbReadTable(con, "Trial_Ids") %>%
    select(ids = input$registry_remove) %>%
    drop_na() %>%
    arrange(str_remove_all(ids, "[A-Z]|-"))

  updateSelectInput(session, "ID_remove", choices = choices_list)

})

#SQL query to remove all lines with this trial
sql_delete <- "DELETE FROM Trial_Ids WHERE ?ColID = ?ID_Selected"

exp_delete <- reactive({
  sqlInterpolate(
    con,
    sql_delete,
    ColID = SQL(case_when(input$registry_remove == "NIHR_Ids" ~ "REPLACE(NIHR_Ids, '-', '')",
                          TRUE ~ input$registry_remove)),
    ID_Selected = if (input$registry_remove == "NIHR_Ids") {str_replace_all(input$ID_remove, "(/)|(-)", "")} else {input$ID_remove}
    )
})

#SQL to read in relevant rows
sql_archive <- "SELECT * FROM ?Orig_Table WHERE ?ColID = ?ID_Selected"

exp_archive_pull <- reactive({
  sqlInterpolate(
    con,
    sql_archive,
    Orig_Table = SQL(str_sub(input$registry_remove, end=-5)),
    ColID = SQL(case_when(input$registry_remove == "NCT_Ids" ~ "NCTId",
                          input$registry_remove == "NIHR_Ids" ~ "REPLACE(REPLACE(project_id,'-',''),'/','')",
                          input$registry_remove == "ISRCTN_Ids" ~ "ISRCTN_No",
                          input$registry_remove == "EU_Ids" ~ "EU_Ids")),
    ID_Selected = if (input$registry_remove == "NIHR_Ids") {str_replace_all(input$ID_remove, "(/)|(-)", "")} else {input$ID_remove}
  )
})

output$exp_delete <- renderText(exp_delete())
output$exp_archive <- renderText(exp_archive_pull())

observeEvent(input$button_delete, {

  shinybusy::show_modal_spinner(spin = "semipolar", color = "#344feb", text = "Deleting Trial - please wait while the dashboard refreshes in background....")

  dbExecute(con, exp_delete())

  source('Download_Trial_Info_no_PM_or_email.R')

  shinybusy::remove_modal_spinner()

  output$success_delete <- renderText("Trial Deleted! Refresh browser for this to update on the live trial lists")

})

observeEvent(input$button_archive, {

  shinybusy::show_modal_spinner(spin = "semipolar", color = "#344feb", text = "Archiving Trial - please wait while the dashboard refreshes in background....")

  pulled_trial_data <- dbGetQuery(con, exp_archive_pull()) %>%
    slice_max(Query_Date) %>% 
    mutate("Archiving_Comments" = str_remove(paste(Comments, as.character(input$comments_archive), collapse = " "), "NA"))

  #write to db (append)
  dbWriteTable(con, paste0(str_sub(input$registry_remove, end=-5), "_rxv"), pulled_trial_data, append = TRUE)

  dbExecute(con, exp_delete())

  source('Download_Trial_Info_no_PM_or_email.R')
  
  shinybusy::remove_modal_spinner()

  #return some success message
  output$success_archive <- renderText("Trial Successfully Archived. It should disappear from live lists and appear in archive on browser refresh")

})

```

### Trial Comments

Select trial and amend comments in the box below

``` {r TrialComments}

inputPanel(
    radioButtons(
      "registry_comment",
      label = "Registry",
      choices = c(
        "Clinicaltrials.gov" = "NCT_Ids",
        "ISRCTN" = "ISRCTN_Ids",
        "NIHR" = "NIHR_Ids",
        "Clinicaltrials.eu" = "EU_Ids"
      )
    ),
    selectInput('ID_comment',
                label = 'Select Trial ID reference number',
                choices = ""),
    textAreaInput("trial_comments", label = "Comments", placeholder = "Trial Comments", resize = "both"),
    actionButton("button_comment", "Amend Comments")
  )

mainPanel(
  textOutput("success_comment")
  )

observeEvent(input$registry_comment, {

  choices_list <- dbReadTable(con, "Trial_Ids") %>%
    select(ids = input$registry_comment) %>%
    drop_na() %>%
    arrange(str_remove_all(ids, "[A-Z]|-"))

  updateSelectInput(session, "ID_comment", choices = choices_list)
  
})

sql_comments_pull <- "SELECT Comments FROM ?Orig_Table WHERE [?ColID] = ?comment_id AND Query_Date IN (SELECT max(Query_Date) FROM ?Orig_Table)"

exp_comment_pull <- reactive({
    sqlInterpolate(
      con,
      sql_comments_pull,
      Orig_Table = SQL(str_sub(input$registry_comment, end=-5)),
      ColID = SQL(case_when(input$registry_comment == "NCT_Ids" ~ "NCTId",
                          input$registry_comment == "NIHR_Ids" ~ "project_id",
                          input$registry_comment == "ISRCTN_Ids" ~ "ISRCTN_No",
                          input$registry_comment == "EU_Ids" ~ "EU_Ids")),
      comment_id = input$ID_comment
  )
})

pulled_comments <- reactive({
  dbGetQuery(con, exp_comment_pull()) %>% as.character()
  })  
  
output$comment_sql <- renderText(exp_comment_pull())
output$fetch_comment_SQL <- renderText(pulled_comments())

observeEvent(input$ID_comment, {
  
  updateTextAreaInput(session, "trial_comments", value = pulled_comments())
  
})


observeEvent(input$button_comment, {
  
  #Add spinner
  show_modal_spinner(spin = "semipolar", color = "#344feb", text = "Amending Comments - please wait while the dashboard refreshes in background....")
  
  #Take contents of button
  comment_text <- input$trial_comments
  
  #Derive SQL to insert into table
  comment_insert_sql <- "UPDATE ?TabID SET Comments = ?comment_text WHERE ?ID_name == ?id_no"
  
  update_comment_sql <- 
    sqlInterpolate(con,
                   comment_insert_sql,
                   TabID = SQL(str_sub(input$registry_comment, end=-5)),
                   comment_text = comment_text,
                   ID_name = SQL(case_when(input$registry_comment == "NCT_Ids" ~ "NCTId",
                          input$registry_comment == "NIHR_Ids" ~ "project_id",
                          input$registry_comment == "ISRCTN_Ids" ~ "ISRCTN_No",
                          input$registry_comment == "EU_Ids" ~ "EU_Ids")),
                   id_no = input$ID_comment
                   )
  
  #Action SQL
  dbExecute(con, update_comment_sql)
  
  #Remove spinner
  remove_modal_spinner()

  #return some success message
  output$success_comment <- renderText("Comments Successfully Updated - please refresh dashboard to see updated comments")

  
})

```


Archived Trials
======================================================

Row {.tabset .tabset-fade}
--------------------------------------------------------



### ClinicalTrials.gov Archive

``` {r CG.govarchive}

dbReadTable(con, "NCT_rxv") %>%
  mutate(across(.fns = clean_UTF),
         `Archive Date` = as_date(as.numeric(Query_Date))) %>% 
  select(
         -SeeAlsoLinkURL,
         -Query_Date,
         ) %>% 
  select(`Archive Date`,
         everything(),
         `Archiving Comments` = Archiving_Comments) %>% 
  rename(
    "Guideline" = Guideline.number,
    `NCT ID` = NCTId,
    `Org Study ID` = OrgStudyId,
    Title = BriefTitle,
    Status = OverallStatus,
    `Primary Completion Date` = PrimaryCompletionDate,
    `Completion Date` = CompletionDate,
    `Results Submit Date` = ResultsFirstSubmitDate,
    `Results Post Date` = ResultsFirstPostDate,
    `Last Update` = LastUpdatePostDate
  ) %>%
  distinct() |> 
  datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")

```

### ISRCTN Archive

```{r ISRCTNarchivetable}

dbReadTable(con, "ISRCTN_rxv") %>%
  mutate(across(.fns = clean_UTF),
         `Archive Date` = as_date(as.numeric(Query_Date))) %>% 
  select(-Query_Date) %>% 
  select(`Archive Date`,
         everything()) %>% 
  rename(
    "Program or Guideline" = Guideline.number,
    `ISRCTN ID` = ISRCTN_No,
    Title = Public_Title,
    `Scientific Title` = Scientific_Title,
    `Recruitment Status` = Recruitment_Status,
    `Results completed date` = Results_date_completed,
    `Results URL` = Results_url_link,
    `Results summary` = Results_summary,
    `Results posted date` = Results_date_posted,
    `Results published date` = Results_date_first_publication,
    `Archiving Comments` = Archiving_Comments
  ) %>%
  distinct() |> 
  datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")

```

### NIHR Archive

``` {r NIHRarchivetable}

dbReadTable(con, "NIHR_rxv") %>%
  mutate(across(.fns = clean_UTF),
         `Archive Date` = as_date(as.numeric(Query_Date))) %>% 
  select(-Query_Date) %>% 
  select(`Archive Date`,
         everything()) %>% 
  rename(
    "Program or Guideline" = Guideline.number,
    `NIHR ID` = project_id,
    `Project Title` = project_title,
    Status = project_status,
    `End Date` = end_date,
    `Archiving Comments` = Archiving_Comments
  ) %>%
  distinct() |> 
  datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")

```

### EU Archive

``` {r EUarchivetable}

dbReadTable(con, "EU_rxv") %>%
  select(-a31_title_of_the_trial_for_lay_people_in_easily_understood_ie_nontechnical_language, -EU_Ids
  ) %>%
  mutate(across(.fns = clean_UTF),
         `Archive Date` = as_date(as.numeric(Query_Date))) %>% 
  select(-Query_Date) %>% 
  rename(
    "Program or Guideline" = Guideline.number,
    `Clinicaltrials.eu ID` = `X_id`,
    `End of Trial Status` = p_end_of_trial_status,
    Title = a3_full_title_of_the_trial,
    `Abbreviated Title` = a32_name_or_abbreviated_title_of_the_trial_where_available,
    `Sponsor ID` = a41_sponsors_protocol_code_number,
    `Archiving Comments` = Archiving_Comments
  ) %>%
  distinct() |> 
  datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")

```
