---
title: "Trial Tracker Dashboard"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    theme:
      version: 5
      bootswatch: flatly
      "enable-dark-mode": false
runtime: shiny
---

```{r setup, context = "server", echo=FALSE, include=FALSE}

db_path <- file.path("inst", "extdata", "RSQLite_data", "TrialTracker-db.sqlite")
main_con <- DBI::dbConnect(RSQLite::SQLite(), db_path)
trial_id_df <- DBI::dbReadTable(main_con, "Trial_Ids")

# Store the db's modified time (POSIXct)
last_refreshed <- reactiveVal({
  if (file.exists(db_path)) file.info(db_path)$mtime
  else as.POSIXct(NA_real_, origin = "1970-01-01", tz = "UTC")
})

# Poll the DB file periodically and refresh the reactive timestamp
observe({
  invalidateLater(60 * 1000, session)  # every 60s; tie timer to the session
  if (file.exists(db_path)) {
    new_ts <- file.info(db_path)$mtime
    # Only update if it actually changed (avoids unnecessary reactivity)
    if (!identical(new_ts, last_refreshed())) last_refreshed(new_ts)
  }
})

# Regex patterns
NCT_pattern <- "^NCT[0-9]{8}$"
EU_pattern <- "^[0-9]{4}-[0-9]{6}-[0-9]{2}$"
ISRCTN_pattern <- "^ISRCTN[0-9]{8}$"
NIHR_pattern <- "(NIHR[0-9]{0,6})|(RP-PG-[0-9]{4}-[0-9]{4,5})|([0-9]{2,3}[/-][0-9]{2,4}[/-][0-9]{2,4})|(^ICA-.*-[0-9]{3})"

# Helper functions (non-reactive and used for rendering UI)

# Clean UTF function
clean_utf8 <- function(x){
  iconv(x, "UTF-8", "UTF-8", sub = "")
}

# Render pubmed function
render_pubmed_table <- function(table_name) {
  if (!table_name %in% DBI::dbListTables(main_con)) return(NULL)

  DBI::dbReadTable(main_con, table_name) |>
    dplyr::mutate(across(everything(), .fns = clean_utf8)) |>
    dplyr::mutate(
      Query_Date = format(as.Date(as.numeric(Query_Date), origin = "1970-01-01"), "%Y/%m/%d"),
      abstract = stringr::str_trunc(abstract, 200L)
    ) |>
    dplyr::rename(
      `Query Date` = Query_Date,
      `Trial ID` = ID,
      `Publication DOI` = doi,
      Title = title,
      Abstract = abstract,
      Journal = jabbrv,
      Condition = `Short..working.title.`,
      Guideline = Guideline.number
    ) |>
    dplyr::select(
      Program, Guideline, `Query Date`, `Trial ID`, pmid,
      `Publication DOI`, Title, Abstract, Journal, Condition
    ) |>
    dplyr::distinct() |>
    dplyr::arrange(dplyr::desc(`Query Date`)) |>
    DT::datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
}

```

```{css, echo=FALSE}
#button_download_dbs.btn,
#downloadtemplate.btn {
  width: auto !important;
  min-width: 0;
}
```

Live Trial Info
======================================================

**`r textOutput("last_refreshed_txt_live", inline = TRUE)`**

Row {.tabset .tabset-fade}
--------------------------------------------------------

### ClinicalTrials.gov

```{r CTGlive}
DT::dataTableOutput("live_trial_table_nct")
```

### ISRCTN

```{r ISCTNlive}
DT::dataTableOutput("live_trial_table_isrctn")
```

### NIHR

```{r NIHRlive}
DT::dataTableOutput("live_trial_table_nihr")
```

### Clinicaltrials.eu

```{r EUlive}
DT::dataTableOutput("live_trial_table_eu")
```

Recent Status Changes
======================================================

**`r textOutput("last_refreshed_txt_recent", inline = TRUE)`**

**Changes are from 31 days ago**

Row {.tabset .tabset-fade}
--------------------------------------------------------

### ClinicalTrials.gov

```{r NCTmonthlychange}
DT::dataTableOutput("nct_monthly_change")
```

### ISRCTN

```{r ISRCTNmonthlychange}
DT::dataTableOutput("isrctn_monthly_change")
```

### NIHR

```{r NIHRmonthlychange}
DT::dataTableOutput("nihr_monthly_change")
```

### Clinicaltrials.eu

```{r Clinicaltrialseumonthlychange}
DT::dataTableOutput("clinicaltrialseu_monthly_change")
```

No Changes in Last 6m
======================================================

**`r textOutput("last_refreshed_txt_nochg", inline = TRUE)`**

Row {.tabset .tabset-fade}
--------------------------------------------------------

### ClinicalTrials.gov

```{r nochangeCTG}
DT::dataTableOutput("no_change_nct")
```

### ISRCTN

```{r nochangeISRCTN}
DT::dataTableOutput("no_change_isrctn")
```

### NIHR

```{r nochangeNIHR}
DT::dataTableOutput("no_change_nihr")
```

### Clinicaltrials.eu

```{r nochangeEU}
DT::dataTableOutput("no_change_cteu")
```

Pubmed Publications
======================================================

**`r textOutput("last_refreshed_txt_pub", inline = TRUE)`**

Row {.tabset .tabset-fade}
--------------------------------------------------------

### ClinicalTrials.gov

```{r CTGpubstable}
render_pubmed_table("NCT_PM")
```

### ISRCTN

```{r ISRCTNpubstable}
render_pubmed_table("ISRCTN_PM")
```

### NIHR

```{r NIHRpubstable}
render_pubmed_table("NIHR_PM")
```

### Clinicaltrials.eu

```{r EUpubstable}
render_pubmed_table("EU_PM")
```

Add/Remove Trials
======================================================

Row {.tabset .tabset-fade}
--------------------------------------------------------

### Add Trial

There are two ways to add trials:

1.  Add one at a time, choosing the relevant registry button, completing the guideline number, trial ID, and URL boxes, then pressing 'add trial'.
2.  Add more than one trial at once by uploading a spreadsheet containing relevant details using the 'choose file' box on the next tab.

**Note that Trial ID reference number must be in the correct format. Eg:**

-   Clinicaltrials.gov - "NCT03883230"
-   ISRCTN - "ISRCTN11735271"
-   NIHR - "14-158-02" or "14/158/02" or "RP-PG-0109-10056"
-   Clinicaltrials.eu - "2007-003673-21" (omit the last two letters designating country)

```{r AddTrialsSideBySide}
# One row with two columns. Uses Bootstrap 5 utilities (works with your theme).
shiny::fluidRow(
  class = "g-3",  # nice gutter spacing

  # =========================
  # LEFT: Add Single Trial
  # =========================
  shiny::column(
    width = 6,
    shiny::div(
      class = "d-flex",
      shiny::div(
        class = "card flex-fill mb-0",
        shiny::div(class = "card-header h5 mb-0", "Add Single Trial"),
        shiny::div(
          class = "card-body",
          shiny::radioButtons(
            "registry_add",
            label = "Select Registry",
            choices = c(
              "Clinicaltrials.gov" = "NCT_Ids",
              "ISRCTN"             = "ISRCTN_Ids",
              "NIHR"               = "NIHR_Ids",
              "Clinicaltrials.eu"  = "EU_Ids"
            )
          ),
          shiny::selectInput(
            "guideline_program_add",
            label   = "Enter program description",
            choices = c("COVID", "IP", "Other"),
            selected = "COVID"
          ),
          shiny::textInput(
            "guideline_reference_add",
            label = "Enter guideline number(s)",
            placeholder = "e.g. CG179"
          ),
          shiny::textInput(
            "ID_add",
            label = "Enter Trial ID reference number",
            placeholder = "e.g. NCT03597750"
          ),
          shiny::textInput(
            "URL_add",
            label = "Paste URL to trial page in registry",
            placeholder = "e.g. https://clinicaltrials.gov/ct2/show/NCT03597750"
          ),
          shiny::actionButton("button_add",
                              label = "Add single trial",
                              icon  = shiny::icon("plus-circle"),
                              class = "btn btn-primary"),
          shiny::div(class = "mt-2", shiny::uiOutput("single_result"))
        )
      )
    )
  ),

  # =========================
  # RIGHT: Add Multiple Trials
  # =========================
  shiny::column(
    width = 6,
    shiny::div(
      class = "d-flex",
      shiny::div(
        class = "card flex-fill mb-0",
        shiny::div(class = "card-header h5 mb-0", "Add Multiple Trials via CSV File"),
        shiny::div(
          class = "card-body",
          # compact, non-stretching download button
          shiny::tags$div(
            class = "d-inline-block mb-2",
            shiny::downloadButton(
              "downloadtemplate",
              label = "Download template",
              class = "btn btn-secondary btn-sm"
            )
          ),
          shiny::fileInput(
            "uploadtemplate",
            label = "Upload completed template",
            multiple = FALSE,
            accept = ".csv"
          ),
          shiny::actionButton("button_add_multi",
                              label = "Add trial spreadsheet",
                              icon  = shiny::icon("file-upload"),
                              class = "btn btn-primary"),
          shiny::div(
            class = "mt-3",
            shiny::uiOutput("multi_result"),
            shiny::textOutput("multi_error"),
            shiny::textOutput("multi_fail"),
            shiny::textOutput("multi_success")
          )
        )
      )
    )
  )
)
```

### Remove or Archive Trial

Select relevant registry and trial ID reference number below, along with any archiving comments.

'Archiving' moves the trial information from the live lists to the relevant archived trials list, where it will no longer be updated. 'Deleting' will remove the trial from the live lists and information will not be stored

```{r Removetab}
shiny::fluidRow(class = "g-3", shiny::column(width = 12, shiny::div(
  class = "card",
  shiny::div(class = "card-header h5 mb-0", "Remove or Archive Trial"),
  shiny::div(
    class = "card-body",
    
    # Inputs
    shiny::fluidRow(
      shiny::column(
        width = 4,
        shiny::radioButtons(
          "registry_remove",
          label = "Registry",
          choices = c(
            "Clinicaltrials.gov" = "NCT_Ids",
            "ISRCTN"             = "ISRCTN_Ids",
            "NIHR"               = "NIHR_Ids",
            "Clinicaltrials.eu"  = "EU_Ids"
          )
        )
      ),
      shiny::column(
        width = 8,
        shiny::selectInput("ID_remove", label = "Select Trial ID reference number", choices = ""),
        shiny::textAreaInput(
          "comments_archive",
          label = "Archive Comments",
          placeholder = "Optional notes for the archive record…",
          rows = 2,
          resize = "vertical"
        )
      )
    ),
    
    # Actions (compact, consistent sizing)
    shiny::div(
      class = "d-flex gap-2 mt-2 flex-wrap",
      shiny::actionButton(
        "button_delete",
        "Delete trial",
        icon  = shiny::icon("trash"),
        class = "btn btn-danger btn-sm"
      ),
      shiny::actionButton(
        "button_archive",
        "Archive trial",
        icon  = shiny::icon("archive"),
        class = "btn btn-warning btn-sm"
      ),
      shiny::downloadButton(
        "button_download_dbs",
        label = "Download SQLite data",
        class = "btn btn-secondary btn-sm"
      )
    )
    ,
    
    # Messages
    shiny::div(
      class = "mt-2",
      shiny::textOutput("success_delete"),
      shiny::textOutput("success_archive")
    )
  )
)))
```

Archived Trials
======================================================

Row {.tabset .tabset-fade}
--------------------------------------------------------

### ClinicalTrials.gov Archive

```{r CG.govarchive}

DBI::dbReadTable(main_con, "NCT_rxv") |>
  dplyr::mutate(across(.cols = everything(), .fns = clean_utf8),
    `Archive Date` = lubridate::as_date(as.numeric(Query_Date))
  ) |>
  dplyr::select(
    -SeeAlsoLinkURL,
    -Query_Date
  ) |>
  dplyr::select(`Archive Date`,
    everything(),
    `Archiving Comments` = Archiving_Comments
  ) |>
  dplyr::rename(
    "Guideline" = Guideline.number,
    `NCT ID` = NCTId,
    `Org Study ID` = OrgStudyId,
    Title = BriefTitle,
    Status = OverallStatus,
    `Primary Completion Date` = PrimaryCompletionDate,
    `Completion Date` = CompletionDate,
    `Results Submit Date` = ResultsFirstSubmitDate,
    `Results Post Date` = ResultsFirstPostDate,
    `Last Update` = LastUpdatePostDate
  ) |>
  dplyr::distinct() |>
  DT::datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
```

### ISRCTN Archive

```{r ISRCTNarchivetable}

DBI::dbReadTable(main_con, "ISRCTN_rxv") |>
  dplyr::mutate(across(.cols = everything(), .fns = clean_utf8),
    `Archive Date` = lubridate::as_date(as.numeric(Query_Date))
  ) |>
  dplyr::select(-Query_Date) |>
  dplyr::select(
    `Archive Date`,
    everything()
  ) |>
  dplyr::rename(
    "Program or Guideline" = Guideline.number,
    `ISRCTN ID` = ISRCTN_No,
    Title = Public_Title,
    `Scientific Title` = Scientific_Title,
    `Recruitment Status` = Recruitment_Status,
    `Results completed date` = Results_date_completed,
    `Results URL` = Results_url_link,
    `Results summary` = Results_summary,
    `Results posted date` = Results_date_posted,
    `Results published date` = Results_date_first_publication,
    `Archiving Comments` = Archiving_Comments
  ) |>
  dplyr::distinct() |>
  DT::datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
```

### NIHR Archive

```{r NIHRarchivetable}

DBI::dbReadTable(main_con, "NIHR_rxv") |>
  dplyr::mutate(across(.cols = everything(), .fns = clean_utf8),
    `Archive Date` = lubridate::as_date(as.numeric(Query_Date))
  ) |>
  dplyr::select(-Query_Date) |>
  dplyr::select(
    `Archive Date`,
    everything()
  ) |>
  dplyr::rename(
    "Program or Guideline" = Guideline.number,
    `NIHR ID` = project_id,
    `Project Title` = project_title,
    Status = project_status,
    `End Date` = end_date,
    `Archiving Comments` = Archiving_Comments
  ) |>
  dplyr::distinct() |>
  DT::datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
```

### EU Archive

```{r EUarchivetable}

DBI::dbReadTable(main_con, "EU_rxv") |>
  dplyr::select(-a31_title_of_the_trial_for_lay_people_in_easily_understood_ie_nontechnical_language, -EU_Ids) |>
  dplyr::mutate(across(.cols = everything(), .fns = clean_utf8),
    `Archive Date` = lubridate::as_date(as.numeric(Query_Date))
  ) |>
  dplyr::select(-Query_Date) |>
  dplyr::rename(
    "Program or Guideline" = Guideline.number,
    `Clinicaltrials.eu ID` = `X_id`,
    `End of Trial Status` = p_end_of_trial_status,
    Title = a3_full_title_of_the_trial,
    `Abbreviated Title` = a32_name_or_abbreviated_title_of_the_trial_where_available,
    `Sponsor ID` = a41_sponsors_protocol_code_number,
    `Archiving Comments` = Archiving_Comments
  ) |>
  dplyr::distinct() |>
  DT::datatable(options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
```

```{r ServerCodeUpdates , context = "server"}

# Inititalise reactive vals for live trial info tables
nct_data <- shiny::reactiveVal(DBI::dbReadTable(main_con, "NCT"))
isrctn_data <- shiny::reactiveVal(DBI::dbReadTable(main_con, "ISRCTN"))
eu_data <- shiny::reactiveVal(DBI::dbReadTable(main_con, "EU"))
nihr_data <- shiny::reactiveVal(DBI::dbReadTable(main_con, "NIHR"))

# Helper to render a "last refreshed" string into a given output ID
render_last_refreshed <- function(id) {
  output[[id]] <- shiny::renderText({
    ts <- last_refreshed()
    if (is.null(ts) || is.na(ts)) return("Unknown")

    # Display in UK local time (BST/GMT) and UTC
    utc <- format(ts, "%Y-%m-%d %H:%M",       tz = "UTC")

    paste0("🔄 Last refreshed at: ",
           utc,
           " UTC)")
  })
}

# Create multiple refresh outputs for each page
render_last_refreshed("last_refreshed_txt_live")
render_last_refreshed("last_refreshed_txt_recent")
render_last_refreshed("last_refreshed_txt_nochg")
render_last_refreshed("last_refreshed_txt_pub")

# Central refresh function
refresh_all_data <- function() {
  
  #Call Update Script
  trialtracker::download_trial_info_wrapper_no_pm_or_email()

  #Update reactives with new sqlite tables
  nct_data(DBI::dbReadTable(main_con, "NCT"))
  isrctn_data(DBI::dbReadTable(main_con, "ISRCTN"))
  eu_data(DBI::dbReadTable(main_con, "EU"))
  nihr_data(DBI::dbReadTable(main_con, "NIHR"))

  last_refreshed(file.info(db_path)$mtime)
}


```

```{r ServerLiveTrialInfo , context = "server"}

# Shared helper for rendering livetrialinfos
render_live_trial_table <- function(data, id_col, ids, rename_list, reorder_cols = NULL, extra_mutate = NULL, extra_filter = NULL) {
  data_filtered <- if (is.function(extra_filter)) extra_filter(data) else data

  date_added_df <- data_filtered |>
    dplyr::summarise(`Date Added` = lubridate::as_date(min(Query_Date - 1L)), .by = {{ id_col }})

  processed <- data_filtered |>
    dplyr::filter({{ id_col }} %in% ids) |>
    dplyr::left_join(date_added_df, by = rlang::as_string(rlang::ensym(id_col))) |>
    dplyr::slice_max(Query_Date, n = 1L, with_ties = TRUE) |>
    dplyr::select(-Query_Date) |>
    dplyr::mutate(across(.cols = everything(), .fns = clean_utf8))

  if (is.function(extra_mutate)) processed <- extra_mutate(processed)

  processed <- processed |>
    dplyr::rename(!!!rename_list)

  if (!is.null(reorder_cols)) {
    processed <- processed |>
      dplyr::select(dplyr::all_of(reorder_cols))
  }

  processed |>
    dplyr::arrange(desc(`Date Added`)) |>
    dplyr::distinct()
}

# Live trial status tables
output$live_trial_table_nct <- DT::renderDT({
  
  req(main_con, trial_id_df, nct_data())

  render_live_trial_table(
    data = nct_data(),
    id_col = NCTId,
    ids = trial_id_df$NCT_Ids,
    rename_list = c(
      Guideline = "Guideline.number",
      `NCT ID` = "NCTId",
      `Org Study ID` = "OrgStudyId",
      Title = "BriefTitle",
      Status = "OverallStatus",
      `Primary Completion Date` = "PrimaryCompletionDate",
      `Completion Date` = "CompletionDate",
      `Results Submit Date` = "ResultsFirstSubmitDate",
      `Results Post Date` = "ResultsFirstPostDate",
      `Last Update` = "LastUpdatePostDate"
    ),
    reorder_cols = c("Program", "Guideline", "Date Added", "NCT ID", "Org Study ID", "Title", "Status",
                     "Primary Completion Date", "Completion Date", "Results Submit Date", "Results Post Date", "Last Update"),
    extra_mutate = ~ dplyr::mutate(., across(PrimaryCompletionDate:LastUpdatePostDate,
                                ~ lubridate::as_date(lubridate::parse_date_time(., c("ymd", "bdy"), truncated = 1))))
  )
}, options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
output$live_trial_table_isrctn <- DT::renderDT({
  
  req(main_con, trial_id_df, isrctn_data())

  render_live_trial_table(
    data = isrctn_data(),
    id_col = ISRCTN_No,
    ids = trial_id_df$ISRCTN_Ids,
    rename_list = c(
      Guideline = "Guideline.number",
      `ISRCTN ID` = "ISRCTN_No",
      Title = "Public_Title",
      `Scientific Title` = "Scientific_Title",
      `Recruitment Status` = "Recruitment_Status",
      `Results URL` = "Results_url_link",
      `Results summary` = "Results_summary"
    ),
    reorder_cols = c("Program", "Guideline", "Date Added", "URL", "ISRCTN ID", "Title", "Acronym",
                     "Scientific Title", "Recruitment Status", "Results URL", "Results summary",
                     "Results_date_completed", "Results_date_posted", "Results_date_first_publication"),
    extra_mutate = ~ dplyr::mutate(.,
      `Results_date_completed` = lubridate::dmy(Results_date_completed),
      `Results_date_posted` = lubridate::dmy(Results_date_posted),
      `Results_date_first_publication` = lubridate::dmy(Results_date_first_publication)
    )
  )
}, options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
output$live_trial_table_nihr <- DT::renderDT({
  
  req(main_con, trial_id_df, nihr_data())

  render_live_trial_table(
    data = nihr_data(),
    id_col = project_id,
    ids = trial_id_df$NIHR_Ids,
    rename_list = c(
      Guideline = "Guideline.number",
      `NIHR ID` = "project_id",
      `Project Title` = "project_title",
      Status = "project_status",
      `End Date` = "end_date"
    ),
    reorder_cols = c("Program", "Guideline", "Date Added", "NIHR ID", "Project Title", "Status", "End Date"),
    extra_filter = ~ dplyr::mutate(., project_id_filter = stringr::str_replace_all(project_id, "[^\\d]", "")) |>
                   dplyr::filter(project_id_filter %in% stringr::str_replace_all(trial_id_df$NIHR_Ids, "[^\\d]", "")) |>
                   dplyr::select(-project_id_filter)
  )
}, options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
output$live_trial_table_eu <- DT::renderDT({
  
  req(main_con, trial_id_df, eu_data())

  render_live_trial_table(
    data = eu_data(),
    id_col = EU_Ids,
    ids = trial_id_df$EU_Ids,
    rename_list = c(
      Guideline = "Guideline.number",
      `Clinicaltrials.eu ID` = "X_id",
      `End of Trial Status` = "p_end_of_trial_status",
      Title = "a3_full_title_of_the_trial",
      `Abbreviated Title` = "a32_name_or_abbreviated_title_of_the_trial_where_available",
      `Sponsor ID` = "a41_sponsors_protocol_code_number"
    ),
    reorder_cols = c("Program", "Guideline", "Date Added", "Clinicaltrials.eu ID", "Title",
                     "Abbreviated Title", "End of Trial Status", "Sponsor ID"),
    extra_filter = ~ dplyr::mutate(., short_id = stringr::str_sub(X_id, 1L, 14L)) |>
                   dplyr::filter(short_id %in% trial_id_df$EU_Ids) |>
                   dplyr::select(-short_id, -a31_title_of_the_trial_for_lay_people_in_easily_understood_ie_nontechnical_language, -EU_Ids)
  )
}, options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
```

```{r ServerRecentStatusChanges , context = "server"}

# Variable for cutoff date (31 days)
cutoff_date <- Sys.Date() - 31L

# Helper function to generate old and new dfs for changes
get_new_old_df <- function(data, id_col, ids) {
  new_df <- data |>
    dplyr::filter({{ id_col }} %in% ids) |>
    dplyr::slice_max(Query_Date, n = 1L, with_ties = TRUE)

  old_df <- data |>
    dplyr::filter(Query_Date <= cutoff_date, {{ id_col }} %in% ids) |>
    dplyr::slice_max(Query_Date, n = 1L, with_ties = TRUE)

  list(new = new_df, old = old_df)
}

# Recent Status Changes Tables
output$nct_monthly_change <- DT::renderDT({
  
  req(main_con, trial_id_df, nct_data())

  dfs <- get_new_old_df(nct_data(), NCTId, trial_id_df$NCT_Ids)

  compareDF::compare_df(
    dfs$new,
    dfs$old,
    group_col = c("Guideline.number", "NCTId"),
    exclude = c("Query_Date", "Condition", "BriefTitle", "Acronym", "PrimaryCompletionDate", "ResultsFirstSubmitDate", "SeeAlsoLinkURL"),
    stop_on_error = FALSE
  )$comparison_df |>
    dplyr::left_join(dfs$new |> dplyr::select(BriefTitle, Program, Guideline.number, URL, NCTId, Condition, ResultsFirstSubmitDate, Acronym),
                     by = c("Program", "Guideline.number", "URL", "NCTId")) |>
    dplyr::mutate(
      URL2 = paste0("https://clinicaltrials.gov/ct2/show/", NCTId),
      Title = stringr::str_trunc(BriefTitle, 80L),
      Condition = stringr::str_trunc(Condition, 30L)
    ) |>
    dplyr::mutate(across(everything(), .fns = clean_utf8)) |>
    dplyr::mutate(across(c(CompletionDate:LastUpdatePostDate),
                         ~ lubridate::as_date(lubridate::parse_date_time(.x, c("ymd", "bdy"), truncated = 1L)))) |>
    dplyr::select(Change = chng_type, Program, Guideline = Guideline.number, URL = URL2, Acronym, Title, Condition,
                  Status = OverallStatus, `Completion Date` = CompletionDate,
                  `Results Submit Date` = ResultsFirstSubmitDate,
                  `Last Update Date` = LastUpdatePostDate) |>
    dplyr::distinct()
}, options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
output$isrctn_monthly_change <- DT::renderDT({
  
  req(main_con, trial_id_df, isrctn_data())

  dfs <- get_new_old_df(isrctn_data(), ISRCTN_No, trial_id_df$ISRCTN_Ids)

  compareDF::compare_df(
    dfs$new,
    dfs$old,
    group_col = c("Guideline.number", "ISRCTN_No"),
    exclude = c("Query_Date"),
    stop_on_error = FALSE
  )$comparison_df |>
    dplyr::left_join(dfs$new) |>
    dplyr::mutate(
      Title = stringr::str_trunc(Scientific_Title, 75L),
      across(everything(), .fns = clean_utf8),
      Results_date_completed = lubridate::dmy(Results_date_completed),
      Results_date_posted = lubridate::dmy(Results_date_posted),
      Results_date_first_publication = lubridate::dmy(Results_date_first_publication)
    ) |>
    dplyr::select(Change = chng_type, Program, Guideline = Guideline.number, URL, Acronym, Title,
                  Status = Recruitment_Status, `Results URL` = Results_url_link, `Results Summary` = Results_summary,
                  `Results Completed` = Results_date_completed, `Results Posted` = Results_date_posted,
                  `Results Published` = Results_date_first_publication) |>
    dplyr::distinct()
}, options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
output$nihr_monthly_change <- DT::renderDT({
  
  req(main_con, trial_id_df, nihr_data())

  trial_ids <- stringr::str_replace_all(trial_id_df$NIHR_Ids, "[^\\d]", "")

  dfs <- get_new_old_df(
    nihr_data() |> dplyr::mutate(project_id_filter = stringr::str_replace_all(project_id, "[^\\d]", "")),
    project_id_filter,
    trial_ids
  )

  dfs <- lapply(dfs, function(df) df |> dplyr::select(-project_id_filter))

  compareDF::compare_df(
    dfs$new,
    dfs$old,
    group_col = c("Guideline.number", "project_id"),
    exclude = c("Query_Date"),
    stop_on_error = FALSE
  )$comparison_df |>
    dplyr::left_join(dfs$new) |>
    dplyr::mutate(
      Title = stringr::str_trunc(project_title, 90L),
      across(everything(), .fns = clean_utf8)
    ) |>
    dplyr::select(
      Change = chng_type,
      Program,
      Guideline = Guideline.number,
      URL,
      `NIHR ID` = project_id,
      Title,
      Status = project_status,
      `End Date` = end_date
    ) |>
    dplyr::distinct()
}, options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
output$clinicaltrialseu_monthly_change <- DT::renderDT({
  
  req(main_con, trial_id_df, eu_data())

  dfs <- get_new_old_df(eu_data(), EU_Ids, trial_id_df$EU_Ids)

  compareDF::compare_df(
    dfs$new,
    dfs$old,
    group_col = c("Guideline.number", "EU_Ids"),
    exclude = c("Query_Date"),
    stop_on_error = FALSE
  )$comparison_df |>
    dplyr::left_join(dfs$new) |>
    dplyr::mutate(
      Title = stringr::str_trunc(a3_full_title_of_the_trial, 90L),
      across(everything(), .fns = clean_utf8)
    ) |>
    dplyr::select(
      Change = chng_type,
      Program,
      Guideline = Guideline.number,
      URL,
      `EU ID` = EU_Ids,
      Status = p_end_of_trial_status,
      Acronym = a32_name_or_abbreviated_title_of_the_trial_where_available,
      Title
    ) |>
    dplyr::distinct()
}, options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
```

```{r ServerNoChangesInLast6M , context = "server"}

# Shared helper for no-change tables
generate_nochange_table <- function(
  data,
  id_col,
  rename_list,
  drop_cols    = NULL,
  reorder_cols = NULL,
  date_cols    = NULL,
  extra_mutate = NULL
) {
  req(data)

  # Be sure Query_Date is Date
  data <- dplyr::mutate(data, Query_Date = lubridate::as_date(Query_Date))

  # Latest date with data
  max_date <- max(data$Query_Date, na.rm = TRUE)

  # Latest date that is at least 6 months older than max_date AND exists in data
  cutoff <- lubridate::add_with_rollback(max_date, -lubridate::period(months = 6L))
  older_ok <- data$Query_Date <= cutoff

  if (any(older_ok, na.rm = TRUE)) {
    old_date <- max(data$Query_Date[older_ok], na.rm = TRUE)
  } else {
    old_date <- as.Date(NA)
  }

  # Snapshots
  current <- dplyr::filter(data, Query_Date == max_date)
  old     <- if (is.na(old_date)) dplyr::slice(current, 0) else dplyr::filter(data, Query_Date == old_date)

  # Date Added (unchanged)
  date_added <- data |>
    dplyr::summarise(`Date Added` = lubridate::as_date(min(Query_Date - 1L)), .by = {{ id_col }})

  # Join on all shared columns EXCEPT Query_Date to identify rows that are unchanged
  by_cols <- setdiff(intersect(names(current), names(old)), "Query_Date")

  joined <- dplyr::inner_join(
      current, old,
      by = by_cols,
      suffix = c(".cur", ".old")
    ) |>
    # Drop duplicated columns created by the join; keep a single copy
    dplyr::select(-dplyr::ends_with(".cur"), -dplyr::ends_with(".old")) |>
    # Attach 'Date Added'
    dplyr::left_join(date_added, by = rlang::as_string(rlang::ensym(id_col))) |>
    dplyr::mutate(across(.cols = dplyr::everything(), .fns = clean_utf8))

  # Parse any date columns for display
  if (!is.null(date_cols) && nrow(joined) > 0) {
    joined <- joined |>
      dplyr::mutate(across(
        dplyr::all_of(date_cols),
        ~ lubridate::as_date(lubridate::parse_date_time(.x, c("ymd", "bdy", "dmy"), truncated = 1))
      ))
  }

  # Optional extra mutate
  if (is.function(extra_mutate)) {
    joined <- extra_mutate(joined)
  }

  # Drop unwanted cols
  if (!is.null(drop_cols)) {
    joined <- dplyr::select(joined, -dplyr::any_of(drop_cols))
  }

  # Rename & reorder
  joined <- joined |>
    dplyr::rename(!!!rename_list)

  if (!is.null(reorder_cols)) {
    joined <- dplyr::select(joined, dplyr::all_of(reorder_cols))
  }

  dplyr::distinct(joined)
}
  
# Tables
output$no_change_nct <- DT::renderDT({
  generate_nochange_table(
    data = nct_data(),
    id_col = NCTId,
    rename_list = c(
      "Guideline" = "Guideline.number",
      `NCT ID` = "NCTId",
      `Org Study ID` = "OrgStudyId",
      Title = "BriefTitle",
      Status = "OverallStatus",
      `Primary Completion Date` = "PrimaryCompletionDate",
      `Completion Date` = "CompletionDate",
      `Results Submit Date` = "ResultsFirstSubmitDate",
      `Results Post Date` = "ResultsFirstPostDate",
      `Last Update` = "LastUpdatePostDate"
    ),
    drop_cols = "SeeAlsoLinkURL",
    reorder_cols = c("Program", "Guideline", "Date Added", "NCT ID", "Org Study ID", "Title", "Status",
                     "Primary Completion Date", "Completion Date", "Results Submit Date", "Results Post Date", "Last Update"),
    date_cols = c("PrimaryCompletionDate", "CompletionDate", "ResultsFirstSubmitDate", "ResultsFirstPostDate", "LastUpdatePostDate")
  )
}, options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
output$no_change_isrctn <- DT::renderDT({
  generate_nochange_table(
    data = isrctn_data(),
    id_col = ISRCTN_No,
    rename_list = c(
      "Guideline" = "Guideline.number",
      `ISRCTN ID` = "ISRCTN_No",
      Title = "Public_Title",
      `Scientific Title` = "Scientific_Title",
      `Recruitment Status` = "Recruitment_Status",
      `Results completed date` = "Results_date_completed",
      `Results URL` = "Results_url_link",
      `Results summary` = "Results_summary",
      `Results posted date` = "Results_date_posted",
      `Results published date` = "Results_date_first_publication"
    ),
    reorder_cols = c("Program", "Guideline", "Date Added", "ISRCTN ID", "Title", "Scientific Title",
                     "Recruitment Status", "Results URL", "Results summary",
                     "Results completed date", "Results posted date", "Results published date"),
    extra_mutate = ~ dplyr::mutate(.,
      Results_date_completed = lubridate::dmy(Results_date_completed),
      Results_date_posted = lubridate::dmy(Results_date_posted),
      Results_date_first_publication = lubridate::dmy(Results_date_first_publication)
    )
  )
}, options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
output$no_change_nihr <- DT::renderDT({
  generate_nochange_table(
    data = nihr_data(),
    id_col = project_id,
    rename_list = c(
      "Guideline" = "Guideline.number",
      `NIHR ID` = "project_id",
      `Project Title` = "project_title",
      Status = "project_status",
      `End Date` = "end_date"
    ),
    reorder_cols = c("Program", "Guideline", "Date Added", "NIHR ID", "Project Title", "Status", "End Date")
  )
}, options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
output$no_change_cteu <- DT::renderDT({
  generate_nochange_table(
    data = eu_data() |> dplyr::select(-a31_title_of_the_trial_for_lay_people_in_easily_understood_ie_nontechnical_language, -EU_Ids),
    id_col = X_id,
    rename_list = c(
      "Guideline" = "Guideline.number",
      `Clinicaltrials.eu ID` = "X_id",
      `End of Trial Status` = "p_end_of_trial_status",
      Title = "a3_full_title_of_the_trial",
      `Abbreviated Title` = "a32_name_or_abbreviated_title_of_the_trial_where_available",
      `Sponsor ID` = "a41_sponsors_protocol_code_number"
    ),
    reorder_cols = c("Program", "Guideline", "Date Added", "Clinicaltrials.eu ID", "Title",
                     "Abbreviated Title", "End of Trial Status", "Sponsor ID")
  )
}, options = list(bPaginate = FALSE, scrollY = TRUE), filter = "top")
```

```{r ServerUserInteractions , context = "server"}

#### Functionality to add / remove / archive /comment

### ADD SINGLE TRIAL
  
# SQL template for adding single trial
sql_add <-
  "INSERT INTO Trial_Ids ([Program], [Guideline.number], [URL], [?registry]) VALUES (?program_value, ?Guideline_Reference, ?URL, ?ID)"

# Reactive to create SQL statement to add single trial
exp_add <- shiny::reactive({
  DBI::sqlInterpolate(
    main_con,
    sql_add,
    registry = DBI::SQL(input$registry_add),
    program_value = input$guideline_program_add,
    Guideline_Reference = input$guideline_reference_add,
    URL = stringr::str_trim(input$URL_add),
    ID = stringr::str_trim(input$ID_add)
  )
})

# Single trial add logic
shiny::observeEvent(input$button_add, {
  valid_id_check <-
    stringr::str_detect(
      stringr::str_trim(input$ID_add),
      stringr::str_c(NCT_pattern, EU_pattern, ISRCTN_pattern, NIHR_pattern, sep = "|")
    )

  if (valid_id_check) {
    shinybusy::show_modal_spinner(spin = "semipolar", color = "#344feb", text = "Adding Trial - please wait while the dashboard refreshes in background....")

    DBI::dbExecute(main_con, exp_add())

    refresh_all_data()

    shinybusy::remove_modal_spinner()

    output$single_result <- shiny::renderUI({
      shiny::HTML(as.character(div(
        style = "color: green;",
        "Trial Added!"
      )))
    })
  } else if (!valid_id_check) {
    output$single_result <- shiny::renderUI({
      shiny::HTML(as.character(div(
        style = "color: red;",
        "Error - Invalid trial ID reference number, please check ID against the above approved formats"
      )))
    })
  }
})

## ADD MULTIPLE TRIALS

# Function to allow downloading of template
output$downloadtemplate <- shiny::downloadHandler(
  filename = function() {
    "trialuploadtemplate.csv"
  },
  content = function(file) {
    readr::write_csv(
      readr::read_csv("trialuploadtemplate.csv",
        col_types = readr::cols(.default = readr::col_character())
      ),
      file,
      na = ""
    )
  }
)

# Reactive for multiple uploads
to_add <- shiny::reactive({
  req(input$uploadtemplate)
  readr::read_csv(input$uploadtemplate$datapath,
                  col_types = readr::cols(.default = readr::col_character()))
})

# Multiple upload logic
shiny::observeEvent(input$uploadtemplate, {
  df <- to_add()
  NCT_check    <- stringr::str_detect(tidyr::replace_na(df$NCT_Ids, ""), NCT_pattern)
  EU_check     <- stringr::str_detect(tidyr::replace_na(df$EU_Ids, ""), EU_pattern)
  ISRCTN_check <- stringr::str_detect(tidyr::replace_na(df$ISRCTN_Ids, ""), ISRCTN_pattern)
  NIHR_check   <- stringr::str_detect(tidyr::replace_na(df$NIHR_Ids, ""), NIHR_pattern)
  Valid_ID     <- NCT_check | EU_check | ISRCTN_check | NIHR_check

  errors <- which(!Valid_ID)

  ## Commented out as only used for debugging
  # output$errors <- shiny::renderText({
  #   paste0("errors = ", as.character(errors))
  # })
  # output$errors_length <- shiny::renderText({
  #   paste0("errors_length = ", as.character(length(errors)))
  # })

  if (length(errors) > 0L) {
    output$multi_result <- shiny::renderText({
      shiny::HTML(as.character(div(
        style = "color: red;",
        paste(
          "ERROR - Missing or incorrect Trial ID on line(s)", as.character(errors),
          ", please correct these IDs and reupload the file"
        )
      )))
    })
  } else if (length(errors) == 0L) {
    output$multi_result <- shiny::renderText({
      shiny::HTML(as.character(div(
        style = "color: green;",
        "File has passed input checks and is ready for upload"
      )))
    })
  }
})
shiny::observeEvent(input$button_add_multi, {
  NCT_check <- stringr::str_detect(tidyr::replace_na(to_add()$NCT_Ids, ""), NCT_pattern)
  EU_check <- stringr::str_detect(tidyr::replace_na(to_add()$EU_Ids, ""), EU_pattern)
  ISRCTN_check <- stringr::str_detect(tidyr::replace_na(to_add()$ISRCTN_Ids, ""), ISRCTN_pattern)
  NIHR_check <- stringr::str_detect(tidyr::replace_na(to_add()$NIHR_Ids, ""), NIHR_pattern)
  Valid_ID <- {
    NCT_check | EU_check | ISRCTN_check | NIHR_check
  }
  multi_errors <- which(!Valid_ID)

  ## Commented out as only used for debugging
  # output$multi_errors <- shiny::renderText({
  #   paste0("multi_errors = ", as.character(multi_errors))
  # })
  # output$multi_errors_length <- shiny::renderText({
  #   paste0("multi_errors_length = ", as.character(length(multi_errors)))
  # })

  if (length(multi_errors) == 0L) {
    shinybusy::show_modal_spinner(spin = "semipolar", color = "#344feb", text = "Adding Trials - please wait while the dashboard refreshes in background....")

    DBI::dbAppendTable(main_con, "Trial_Ids", to_add())

    refresh_all_data()

    shinybusy::remove_modal_spinner()

    output$multi_result <- shiny::renderText({
      shiny::HTML(as.character(div(
        style = "color: green;",
        "Multiple Trials Added! - please refresh browser to see trial details on Live Trial Info tab"
      )))
    })
  } else if (length(multi_errors) > 0L) {
    output$multi_result <- shiny::renderText({
      shiny::HTML(as.character(div(
        style = "color: red;",
        "Error - Please correct errors in trial ID numbers on upload sheet before resubmitting"
      )))
    })
  }
})

#### REMOVE OR ARCHIVE TRIALS

# SQL template for deleting trial id from Trial_Ids
sql_delete <- "DELETE FROM Trial_Ids WHERE ?ColID = ?ID_Selected"

# Reactive to pull id to insert into SQL delete request
exp_delete <- shiny::reactive({
  DBI::sqlInterpolate(
    main_con,
    sql_delete,
    ColID = DBI::SQL(dplyr::case_when(
      input$registry_remove == "NIHR_Ids" ~ "REPLACE(REPLACE(NIHR_Ids, '-', ''),'/','')",
      TRUE ~ input$registry_remove
    )),
    ID_Selected = if (input$registry_remove == "NIHR_Ids") {
      stringr::str_replace_all(input$ID_remove, "(/)|(-)", "")
    } else {
      input$ID_remove
    }
  )
})

# Render output [used in debugging when enabled in UI]
output$exp_delete <- shiny::renderText(exp_delete())

#Delete logic
shiny::observeEvent(input$button_delete, {
  shinybusy::show_modal_spinner(spin = "semipolar", color = "#344feb", text = "Deleting Trial - please wait while the dashboard refreshes in background....")

  DBI::dbExecute(main_con, exp_delete())

  refresh_all_data()

  shinybusy::remove_modal_spinner()

  output$success_delete <- shiny::renderText("Trial Deleted! Refresh browser for this to update on the live trial lists")
})

#Update remove list
shiny::observeEvent(input$registry_remove, {
  choices_list <- DBI::dbReadTable(main_con, "Trial_Ids") |>
    dplyr::select(ids = input$registry_remove) |>
    tidyr::drop_na() |>
    dplyr::arrange(stringr::str_remove_all(ids, "[A-Z]|-")) |> 
    dplyr::pull(ids)
  
  shiny::updateSelectInput(session, "ID_remove", choices = choices_list)
  
  #output$choices_list <- shiny::renderText(choices_list)
  
})

# SQL template for SQL archive select statement
sql_archive <- "SELECT * FROM ?Orig_Table WHERE ?ColID = ?ID_Selected"

# Reactive for pulling id to insert into SQL archiving request
exp_archive_pull <- shiny::reactive({
  DBI::sqlInterpolate(
    main_con,
    sql_archive,
    Orig_Table = DBI::SQL(stringr::str_sub(input$registry_remove, end = -5L)),
    ColID = DBI::SQL(dplyr::case_when(
      input$registry_remove == "NCT_Ids" ~ "NCTId",
      input$registry_remove == "NIHR_Ids" ~ "REPLACE(REPLACE(project_id,'-',''),'/','')",
      input$registry_remove == "ISRCTN_Ids" ~ "ISRCTN_No",
      input$registry_remove == "EU_Ids" ~ "EU_Ids"
    )),
    ID_Selected = if (input$registry_remove == "NIHR_Ids") {
      stringr::str_replace_all(input$ID_remove, "(/)|(-)", "")
    } else {
      input$ID_remove
    }
  )
})

# Render output [used in debugging when enabled in UI]
output$exp_archive <- shiny::renderText(exp_archive_pull())

#Archive logic
shiny::observeEvent(input$button_archive, {
  shinybusy::show_modal_spinner(spin = "semipolar", color = "#344feb", text = "Archiving Trial - please wait while the dashboard refreshes in background....")

  pulled_trial_data <- DBI::dbGetQuery(main_con, exp_archive_pull()) |>
    dplyr::slice_max(Query_Date) |>
    dplyr::mutate("Archiving_Comments" = stringr::str_remove(paste(Comments, as.character(input$comments_archive), collapse = " "), "NA"))

  # write to db (append)
  DBI::dbWriteTable(main_con, paste0(stringr::str_sub(input$registry_remove, end = -5L), "_rxv"), pulled_trial_data, append = TRUE)

  DBI::dbExecute(main_con, exp_delete())

  refresh_all_data()

  shinybusy::remove_modal_spinner()

  # return some success message
  output$success_archive <- shiny::renderText("Trial Successfully Archived. It should disappear from live lists and appear in archive on browser refresh")
})

# Server code for 'download SQLite databases' button
  
# Function to allow downloading of files
output$button_download_dbs <- shiny::downloadHandler(
  
filename = function() paste0("databases-", Sys.Date(), ".zip"),
  content  = function(file) {
    zip::zipr(
      zipfile = file,
      files   = c("TrialTracker-db.sqlite", "EU_temp_db.sqlite"),
      root    = file.path("inst", "extdata", "RSQLite_data"),
      recurse = FALSE,
      include_directories = FALSE
    )
  }
)
```
